Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2015-12-08 jss/article.tex
Added example of uncorrected test

%multisample_enrichment<-function(Genes_by_sample=NULL,
%                                 maps = ACSNMineR::ACSN_maps, 
%                                 correction_multitest = "BH",
%                                 statistical_test = "fisher",
%                                 min_module_size = 5,
%                                 universe = "map_defined",
%                                 threshold = 0.05,
%                                 cohort_threshold = TRUE,
%                                 alternative = "greater"){
It may be of interest to compare enrichment of pathwways in different cohorts or experiments. For example, enrichment of highly expressed pathways can reveal differences between two cancer types or two cell lines.
To ease such comparisons, \pkg{ACSNMineR} provides a \code{multisample_enrichment} function. It relies on the \code{enrichment} function but takes a list of character vector genes. The name of each element of the list will be assumed to be the name of the sample for further analysis.
Most of the arguments given to \code{multisample_enrichment} are the same as the ones passed to \code{enrichment}. However, the \code{cohort_threshold} is designed to filter out modules which would not pass the significance threshold in all samples.

@@

>>>>

%multisample_enrichment<-function(Genes_by_sample=NULL,
%                                 maps = ACSNMineR::ACSN_maps, 
%                                 correction_multitest = "BH",
%                                 statistical_test = "fisher",
%                                 min_module_size = 5,
%                                 universe = "map_defined",
%                                 threshold = 0.05,
%                                 cohort_threshold = TRUE,
%                                 alternative = "greater"){
It may be of interest to compare enrichment of pathways in different cohorts or experiments. For example, enrichment of highly expressed pathways can reveal differences between two cancer types or two cell lines.
To ease such comparisons, \pkg{ACSNMineR} provides a \code{multisample_enrichment} function. It relies on the \code{enrichment} function but takes a list of character vector genes. The name of each element of the list will be assumed to be the name of the sample for further analysis.
Most of the arguments given to \code{multisample_enrichment} are the same as the ones passed to \code{enrichment}. However, the \code{cohort_threshold} is designed to filter out modules which would not pass the significance threshold in all samples.

@@

The package also includes a use-case that we detail below. Using, \code{genes_test} it is possible to explore the different possibilities of exploration of the maps. We previously computed the p-value of \code{genes_test} with default parameters.
The number of modules which have a p-value below 0.05 was 36, that can be compared to the 49 obtained without correction:
\code{enrichment(genes_test,correction_multitest = FALSE)}
\begin{table}[h!]
  \centering
  \caption{Overview of results from enrichment analysis without correction. Module : name of the module. Module size: size of the module. Genes in module: genes from input which are found in the module. p-value: uncorrected p-value. Test : null hypothesis used, greater is synonym of enrichment.}
  \label{tab:table2}

  \begin{tabular}{l|c|c|c|c}
	\hline
Module & Module size & Genes in module & p-value & Test\\
	\hline
Apoptosis:E2F1 & 5 &  ATM E2F1 EP300 KAT2B  & 1.043478e-08 & greater \\
Apoptosis:G2 M CHECKPOINT & 35  & ATM KAT2B & 2.040546e-02 & greater \\
Apoptosis:WNT CANONICAL & 53 & E2F1 EP300 KAT2B  & 4.984433e-03 & greater \\
	\end{tabular}
\end{table}
